---
title: "PPOL564 Project"
author: "Ella Zhang"
date: "12/2/2020"
output:
  ioslides_presentation:
    incremental: true
    widescreen: true
---

```{r setup, include=FALSE}
reticulate::use_python("/usr/local/bin/python3")
knitr::opts_chunk$set(echo = FALSE)
```

## Problem Statement

- What factors make it more or less likely for a restaurant
  - To be in the Michelin guide?
  - To get a Michelin star?

## Background

- Michelin
  - French tire manufacturer
  - Introduced the star rating system
    - <span style="color:red">One Star:</span> high quality cooking, worth a stop
    - <span style="color:red">Two Stars:</span> excellent cuisine, worth a detour
    - <span style="color:red">Three Stars:</span> exceptional cuisine, worth a special journey
  - Only reviewed five cities in the U.S.
    - Washington, D.C.
    - Chicago
    - New York
    - San Francisco
    - Los Angeles

## Methods

- Web Scraping
  - Yelp: rating, category, price, reviews
  - Wikipedia: list of Michelin starred restaurants
  - Michelin Guide website
- Google Plaves API
  - Rating, menu, reviews, popular times
- Data Wrangling

## Methods

- Data Visualization
  - Bar graph
  - Pie chart
  - Map
- Machine Learning
  - What factors predict whether or not a restaurant will receive a star?
  - Which factor matters the most?

```{python include = FALSE}
import pandas as pd
DC_Yelp = pd.read_csv("Data/Yelp/DC_Yelp_cleaned.csv")
```

## Methods Used

- Web Scraping
  - Yelp
```{python echo = TRUE}
DC_Yelp
```
  - Wikipedia
  - Michelin Guide website

---

```{r, cars, fig.cap="A scatterplot.", echo=FALSE}
plot(cars)
```

## Going to sleep

- Get in bed
- Count sheep
